\LARGE \bf Explicit Knowledge and the Deliberative Layer: Lessons Learned

### 2013-03-22 paper.tex
Added section on Working memory and finish Theory of Mind

The \cite{Warnier2012a}

@@

>>>>

One classical application of this cognitive skills is the so-called
\emph{False-Belief} experiment~\cite{Leslie2000}: a child is asked to watch a
scene where two people, A and B, manipulate objects. Then A leaves and B hides
away one object. When A comes back, we ask the child ``where do you think A
will look for the object?''. Before acquiring a theory of mind, children are
not able to separate their own (true) model of the world (where they know that
the object was hidden) from the model of A, which contains \emph{false beliefs}
on the world (A still thinks the object is at its original position since he
did not see B hiding it). Using seperate knowledge models in the knowledge
base, we have been able to replicate this experience on our
robots~\cite{Warnier2012a}.

@@

The {\sc Oro} server also feature a mechanism to mimic simple forms of
biological memory.  When new statements are inserted in the knowledge base, a
\emph{memory profile} is optionally attached to them.

Three such profiles are predefined: {\tt short term}, {\tt episodic} and {\tt
long term}. They each correspond to a different lifetime for the statements
(respectively 10 seconds, 5 minutes and no time limit). After this duration,
the statements are automatically removed from the knowledge base.

This approach is limited. In particular, \emph{episodic} memory primarily
refers to the semantics of the statements (that is expected to be related to an
event) and not to a specific life duration.

We rely however on this short term memory for a particular use-case:
\emph{active concept}. Some modules, like the natural language processor, use
the {\tt short term} memory profile to mark for a few seconds important
concepts that are currently manipulated by the robot. For example, if a human
asks the robot: ``Give me all red objects'', the human, the \concept{Give}
action, and each red objects that are found are successively marked as
\emph{active concepts} by inserting statements like \stmt{human type
ActiveConcept} in the short-term memory (which can be considered, in this case,
to be a working memory). We use this feature to give a (visual) feedback to the
users.
